================================================================================
 BOSKET'S ALIMENTOS — STEPS TO RUN, TEST, CHECK DATABASE & PUBLISH
 (A world of truly fusion food · 100% Veg)
 Last updated: 11 June 2026 — all 36 end-to-end checks passing
================================================================================


--------------------------------------------------------------------------------
 1. RUN THE SITE LOCALLY IN YOUR BROWSER
--------------------------------------------------------------------------------

QUICK START (one double-click)
------------------------------
Run this file:

    D:\Ketul\Claude_Projects\BosketsAlimentosTools\START-LOCAL-TESTING.bat

It automatically:
  - starts the MariaDB database server (if not already running)
  - starts the website server on port 8088
  - starts the Adminer database GUI on port 8089
  - opens both browser tabs for you

The servers run as MINIMIZED WINDOWS on your taskbar.
Close those windows when you are done testing.

URLS
----
  Website ............ http://127.0.0.1:8088
  Database GUI ....... http://127.0.0.1:8089/adminer.php

WHAT IS RUNNING UNDER THE HOOD (manual start, if ever needed)
-------------------------------------------------------------
  1. Database:
     "C:\Program Files\MariaDB 12.3\bin\mariadbd.exe"
         --defaults-file="C:\Program Files\MariaDB 12.3\data\my.ini"
  2. Website:
     php -S 127.0.0.1:8088 -t D:\Ketul\Claude_Projects\BosketsAlimentosWebSite
  3. Adminer:
     php -S 127.0.0.1:8089 -t D:\Ketul\Claude_Projects\BosketsAlimentosTools


--------------------------------------------------------------------------------
 2. TEST ACCOUNTS
--------------------------------------------------------------------------------

  ROLE         USERNAME                                   PASSWORD
  -----------  -----------------------------------------  ------------
  Admin        admin                                      Admin@12345
  Demo member  maya_fusion                                Demo@1234
  Demo member  leo_cocina / sakura_spice / arjun_tadka    Demo@1234

  Admin Panel: sign in as admin -> avatar menu -> Admin Panel.


--------------------------------------------------------------------------------
 3. SUGGESTED THOROUGH TEST CHECKLIST
--------------------------------------------------------------------------------

TIP: open a normal browser window as one user and a PRIVATE/INCOGNITO window
as another user — then you can watch buddy requests and notifications arrive
in real time between the two.

  [ ] Register a brand-new account (email + password, optional avatar <= 5 MB)
  [ ] Edit profile, change password, try account deletion (Settings page)
  [ ] "Forgot your password?" link on Sign In page
      NOTE: the reset EMAIL cannot be delivered on a local Windows PC
      (no mail server). The flow itself is fully tested and will work
      on Hostinger after you set MAIL_FROM in config.php.
  [ ] Post a New Recipe:
      - Section 1: name + main picture (both mandatory) + story
      - Section 2: type 3 letters of an ingredient -> suggestions appear;
        type a NEW ingredient -> it is added to the master list for everyone
      - Section 3: category / cuisine / origin (same typeahead behaviour)
      - Section 4: add several steps, attach a photo or short video to a step
      - Section 5: verdict / trivia, then Post Recipe
  [ ] React (like/love/yum/wow), comment and share a recipe
      (share = repost to your wall + WhatsApp / Facebook / X / copy link)
  [ ] Post a food story (text + photo) on your own wall
  [ ] Send a BUDDY REQUEST from window A; watch the bell notification in
      window B; accept it; confirm both buddy lists update
  [ ] Check "My Feed" now shows the buddy's wall posts and recipes
  [ ] Confirm a NON-buddy cannot see your wall (buddies-only lock screen)
  [ ] Forum: start a new topic on an existing board; create a NEW board;
      reply and react on someone else's topic
  [ ] Notifications page: click each notification — it should land on the
      right recipe / wall post / topic / buddy page
  [ ] Admin Panel: feature a recipe (star on homepage), hide a comment,
      ban/unban a user, rename a master-list ingredient
  [ ] Mobile view: resize the browser window narrow — header collapses to
      the hamburger menu


--------------------------------------------------------------------------------
 4. CHECKING THE DATABASE
--------------------------------------------------------------------------------

OPTION A — ADMINER (graphical, easiest)
---------------------------------------
  1. Open  http://127.0.0.1:8089/adminer.php
  2. Log in with:
       System ....... MySQL
       Server ....... 127.0.0.1
       Username ..... boskets
       Password ..... Boskets@Local1
       Database ..... boskets
  3. Click any table -> "Select data" to browse rows, edit values,
     or use the "SQL command" link to run your own queries.

OPTION B — COMMAND LINE (quick)
-------------------------------
  In PowerShell:

    & 'C:\Program Files\MariaDB 12.3\bin\mariadb.exe' -u boskets -pBoskets@Local1 boskets

  Example queries:
    SELECT id, username, email, created_at FROM users;
    SELECT id, title, status FROM recipes ORDER BY created_at DESC;
    SELECT * FROM buddies;
    SELECT * FROM notifications ORDER BY id DESC LIMIT 20;
  Type  exit  to leave.

THE 16 TABLES
-------------
  users ................ member accounts (admin flag, ban flag, avatar)
  buddies .............. buddy requests + accepted/rejected status
  recipes .............. recipe header (title, image, story, verdict...)
  recipe_ingredients ... ingredients + quantities per recipe
  recipe_steps ......... step-by-step method incl. optional media
  ingredients .......... MASTER LIST — grows as users type new ones
  categories ........... MASTER LIST (recipe categories)
  cuisines ............. MASTER LIST (cuisine types)
  origins .............. MASTER LIST (recipe origins)
  wall_posts ........... food stories + shared recipes on member walls
  forum_categories ..... forum boards (predefined + user-created)
  forum_topics ......... forum discussions
  comments ............. comments on recipes / wall posts / topics
  reactions ............ like / love / yum / wow on all content
  notifications ........ bell notifications
  password_resets ...... forgot-password tokens (1-hour expiry)


--------------------------------------------------------------------------------
 5. PUBLISHING TO HOSTINGER (summary — full guide in README-DEPLOY.md)
--------------------------------------------------------------------------------

  1. hPanel -> Databases -> MySQL Databases:
     create a database + user + strong password (note all three).

  2. Edit config.php — REPLACE the LOCAL TEST values:
       DB_HOST  -> 'localhost'
       DB_NAME  -> your Hostinger database name  (u123456789_xxxx)
       DB_USER  -> your Hostinger database user
       DB_PASS  -> your Hostinger database password
     Optional but recommended:
       SITE_URL  -> 'https://yourdomain.com'
       MAIL_FROM -> a mailbox on your domain (hPanel -> Emails),
                    used for password-reset emails.

  3. Upload ALL files from the website folder into public_html
     (File Manager zip-upload or FTP). Make sure public_html/index.php exists.
     DO NOT upload anything from the BosketsAlimentosTools folder
     (adminer.php must never go on the live server).

  4. Open  https://yourdomain.com/install.php  -> create your admin account,
     choose whether to seed demo content -> Install.

  5. DELETE install.php from the server immediately afterwards.

  6. hPanel -> Security -> SSL: install the free certificate + Force HTTPS.

  7. hPanel -> Advanced -> PHP Configuration: PHP 8.1+,
     upload_max_filesize 30M, post_max_size 64M.

  8. SEO finishing touches:
     - put your absolute sitemap URL in robots.txt:
         Sitemap: https://yourdomain.com/sitemap.php
     - submit that URL in Google Search Console.

  On the live server, the database is managed via
  hPanel -> Databases -> phpMyAdmin (same tables as listed above).


--------------------------------------------------------------------------------
 KEY LOCAL FILES & CREDENTIALS AT A GLANCE
--------------------------------------------------------------------------------

  Website folder ....... D:\Ketul\Claude_Projects\BosketsAlimentosWebSite
  Tools folder ......... D:\Ketul\Claude_Projects\BosketsAlimentosTools
  Launcher ............. START-LOCAL-TESTING.bat   (in the tools folder)
  Site URL ............. http://127.0.0.1:8088
  DB GUI URL ........... http://127.0.0.1:8089/adminer.php
  Local DB ............. boskets @ 127.0.0.1:3306  (boskets / Boskets@Local1)
  Local admin .......... admin / Admin@12345
  Demo users ........... Demo@1234
  Master prompt ........ PROMPT.TXT
  Deploy guide ......... README-DEPLOY.md

================================================================================
